---
title: "S-SOMAS Pilot-0 IRT"
author: "Douglas Whitaker"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: html_document
---

## CFA

This draws on Matt's code for reading the data and the like. 

```{r include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(cache = TRUE)

```

```{r setup, include=FALSE}
## Loading packages that are needed for the following code

#rm(list = ls(all.names = TRUE)) ### Used to test if code works from beginning without having to knit

library("readxl") # read_excel
library("dplyr") # mutate
library("matrixStats") # rowVars
library("psych") # skew, kurtosi
library("lavaan") # cfa
library("semPlot") 
library("corrplot")
library("eRm")
library("semTools")
library("ltm")
library("kableExtra")
library("MPsychoR")
library("mirt")
library("Gifi")
library("RColorBrewer")
library("unimirt")

# library(GPArotation)
# library(nFactors)
# library(ggplot2)
# library(tidyverse)
# library(kableExtra)
# library(magrittr)
# library(moments)
# library(reshape)
# library(resemble)
# library(likert)
# library(broom)
# library(grid)
# library(patchwork)
# library(kableExtra)
# library(networkD3)

```

# Reading in the Data

We read in the datasets created using the `pilot0_data_cleaning.Rmd` file. 

```{r readdata}
group1 <- read.csv(file = "data/confidential/group1rc.csv")
group2 <- read.csv(file = "data/confidential/group2rc.csv")

```


We now drop the "nrc" columns because we won't use them.

```{r dropnrc}
group1 <- group1[,!grepl("nrc", names(group1))]
group2 <- group2[,!grepl("nrc", names(group2))]
```

# Item Response Theory Analysis

This section will start by closely following Mair (2018) Chapter 4.

## Dimensionality

```{r princaller_res1}
if (packageVersion("MASDERtools") < "0.0.5.1"){
  stop("Update MASDERtools before continuing.")
}
scale_names_group1 <- unique(gsub(pattern = "\\_(.*)", x = names(group1), replacement = "", perl = TRUE))
g1_pc_out <- MASDERtools::princaller(dat = group1, scale.names = scale_names_group1, method = "linear")
print(g1_pc_out)
scale_names_group2 <- unique(gsub(pattern = "\\_(.*)", x = names(group2), replacement = "", perl = TRUE))
g2_pc_out <- MASDERtools::princaller(dat = group2, scale.names = scale_names_group2, method = "linear")
print(g2_pc_out)
```

The following items should be dropped based on the results:

* Group 1
    * Belief: two groups
        * 2rc, 4rc, 5rc, 10rc
        * 1, 3rc, 6, 7, 8, 9
    * Intrinsic: three groups
        * 3, 5, 7
        * 4
        * 1, 2, 6
    * Extrinsic: three groups
        * 6, 7, 8
        * 1, 4, 5
        * 2, 3
    * Utility: three groups
        * 1, 3rc, 5rc, 8rc
        * 2, 4, 6, 7
    * Attain: perhaps three groups
        * 1, 2, 3
        * 4
        * 5, 6, 7
    * Interest: two groups
        * 2, 4, 6, 9
        * 1rc, 3rc, 5, 7rc, 8rc
* Group 2
    * AcadSC: two groups
        * 1, 2, 3, 4, 6
        * 5rc, 7rc, 8rc, 9rc
    * Attain: perhaps three groups
        * 1, 2, 3
        * 4
        * 5, 6, 7
    * StatSC: one group
    * Difficulty: perhaps two groups
        * 1rc, 2, 3, 6rc, 7rc
        * 4rc, 5
    * Expectancy: two groups
        * 1rc, 6rc, 11rc
        * 2, 3, 4, 5, 7, 8, 9, 10
    * Cost: three groups
        * 5
        * 7rc
        * 1, 2, 3rc, 4rc, 6    
        
        
```{r compare_IRT}
comparer_out_g1 <- MASDERtools::comparer(dat = group1, scale.names = scale_names_group1)
comparer_out_g2 <- MASDERtools::comparer(dat = group2, scale.names = scale_names_group2)
``` 


```{r grmer1, include=FALSE}
grmit_g1_out1 <- MASDERtools::grmit(dat = group1, scale.names = scale_names_group1)
itemfit1_out1 <- MASDERtools::itemfitbuilder(grmit_g1_out1)
grmit_g2_out1 <- MASDERtools::grmit(dat = group2, scale.names = scale_names_group2)
itemfit2_out1 <- MASDERtools::itemfitbuilder(grmit_g2_out1)
```

```{r}
itemfit1_out1 %>% 
  kbl() %>%
  kable_paper("hover", full_width = FALSE) %>% 
  column_spec(2:3, color = "white", background = ifelse(abs(itemfit1_out1$z.outfit) > 2, "red", "blue")) %>%
  column_spec(4:5, color = "white", background = ifelse(abs(itemfit1_out1$z.infit) > 2, "red", "blue")) 

itemfit2_out1 %>% 
  kbl() %>%
  kable_paper("hover", full_width = FALSE) %>% 
  column_spec(2:3, color = "white", background = ifelse(abs(itemfit2_out1$z.outfit) > 2, "red", "blue")) %>%
  column_spec(4:5, color = "white", background = ifelse(abs(itemfit2_out1$z.infit) > 2, "red", "blue")) 


```

```{r grmer2, include=FALSE}
grmit_g1_out2 <- MASDERtools::grmit(dat = group1, scale.names = scale_names_group1,
                                    drop.items=list(c(2,4,5,10), # Belief
                                            NULL, # Intrinsic
                                            c(2,3), # Extrinsic
                                            c(2,4,6,7), # Utility
                                            c(1,2,3), # Attain
                                            NULL)) # Interest)
itemfit1_out2 <- MASDERtools::itemfitbuilder(grmit_g1_out2)
grmit_g2_out2 <- MASDERtools::grmit(dat = group2, scale.names = scale_names_group2,
                                    drop.items=list(NULL, # AcadSC
                                            c(1,2), # Attain
                                            NULL, # StatSC
                                            c(4,5), # Difficult
                                            c(1,6,11), # Expectancy
                                            c(5,7))) # Cost)
itemfit2_out2 <- MASDERtools::itemfitbuilder(grmit_g2_out2)
```

```{r grmer3, include=FALSE}
grmit_g1_out3 <- MASDERtools::grmit(dat = group1, scale.names = scale_names_group1[c(1,4,5)],
                                    drop.items=list(c(1,3,6,7,8,9), # Belief
                                                    c(1,3,5,8), # Utility
                                                    c(5,6,7))) # Attain)
itemfit1_out3 <- MASDERtools::itemfitbuilder(grmit_g1_out3)

```

```{r}
itemfit1_out2 %>% 
  kbl() %>%
  kable_paper("hover", full_width = FALSE) %>% 
  column_spec(2:3, color = "white", background = ifelse(abs(itemfit1_out2$z.outfit) > 2, "red", "blue")) %>%
  column_spec(4:5, color = "white", background = ifelse(abs(itemfit1_out2$z.infit) > 2, "red", "blue")) 

itemfit2_out2 %>% 
  kbl() %>%
  kable_paper("hover", full_width = FALSE) %>% 
  column_spec(2:3, color = "white", background = ifelse(abs(itemfit2_out2$z.outfit) > 2, "red", "blue")) %>%
  column_spec(4:5, color = "white", background = ifelse(abs(itemfit2_out2$z.infit) > 2, "red", "blue")) 

itemfit1_out3 %>% 
  kbl() %>%
  kable_paper("hover", full_width = FALSE) %>% 
  column_spec(2:3, color = "white", background = ifelse(abs(itemfit1_out3$z.outfit) > 2, "red", "blue")) %>%
  column_spec(4:5, color = "white", background = ifelse(abs(itemfit1_out3$z.infit) > 2, "red", "blue")) 

```

Now we plot tracelines. 

```{r item_graphs, fig.show = "hold", out.width = "33%"}
MASDERtools::itemplotter(grmit_g1_out1)
MASDERtools::itemplotter(grmit_g1_out2)
MASDERtools::itemplotter(grmit_g1_out3)
MASDERtools::itemplotter(grmit_g1_out2)

```

Now we construct Wright Maps for Group 1.

```{r Wright_g1}

for (i in 1:length(scale_names_group1)){
  tmp_item_symbols <- matrix(rep(49:54, 
                               times = nrow(unimirt::ThurstonianThresh(
                                 grmit_g1_out2[[i]]$mirt.out))),
                              byrow = TRUE, 
                                ncol = (ncol(unimirt::ThurstonianThresh(
                               grmit_g1_out2[[i]]$mirt.out)))-1)
  tmp_item_colours <- matrix(rep(brewer.pal(6, "Dark2"), 
                               times = nrow(unimirt::ThurstonianThresh(
                                 grmit_g1_out2[[i]]$mirt.out))),
                             byrow = TRUE, 
                             ncol = (ncol(unimirt::ThurstonianThresh(
                              grmit_g1_out2[[i]]$mirt.out)))-1)
  tmp_thresh <- unimirt::ThurstonianThresh(grmit_g1_out2[[i]]$mirt.out)
  WrightMap::wrightMap(thetas = grmit_g1_out2[[i]]$personscores,
                       thresholds = tmp_thresh[,-1],
                       main.title = paste("Wright Map with Thurstonian Thresholds for ", scale_names_group1[i], sep = ""),
                       label.items = tmp_thresh[,1],
                       show.thr.lab = FALSE,
                       thr.sym.pch = tmp_item_symbols,
                       thr.sym.cex = 1.5,
                       thr.sym.col.fg = tmp_item_colours)
                       #dim.color = RColorBrewer::brewer.pal(8, "Set1")[i])
}
```

Now we drop Belief 2, 4, 5, and 10.

```{r Wright_g1b}

grmit_g1_out2_dropB2 <- MASDERtools::grmit(dat = group1, 
                                           scale.names = scale_names_group1[1],
                                           drop.items = list(c(2,4,5,10)))


for (i in 1:length(scale_names_group1[1])){
  tmp_item_symbols <- matrix(rep(49:54, 
                               times = nrow(unimirt::ThurstonianThresh(
                                 grmit_g1_out2_dropB2[[i]]$mirt.out))),
                              byrow = TRUE, 
                                ncol = (ncol(unimirt::ThurstonianThresh(
                               grmit_g1_out2_dropB2[[i]]$mirt.out)))-1)
  tmp_item_colours <- matrix(rep(brewer.pal(6, "Dark2"), 
                               times = nrow(unimirt::ThurstonianThresh(
                                 grmit_g1_out2_dropB2[[i]]$mirt.out))),
                             byrow = TRUE, 
                             ncol = (ncol(unimirt::ThurstonianThresh(
                              grmit_g1_out2_dropB2[[i]]$mirt.out)))-1)
  tmp_thresh <- unimirt::ThurstonianThresh(grmit_g1_out2_dropB2[[i]]$mirt.out)
  WrightMap::wrightMap(thetas = grmit_g1_out2_dropB2[[i]]$personscores,
                       thresholds = tmp_thresh[,-1],
                       main.title = paste("Wright Map with Thurstonian Thresholds for ", scale_names_group1[i], sep = ""),
                       label.items = tmp_thresh[,1],
                       show.thr.lab = FALSE,
                       thr.sym.pch = tmp_item_symbols,
                       thr.sym.cex = 1.5,
                       thr.sym.col.fg = tmp_item_colours)
                       #dim.color = RColorBrewer::brewer.pal(8, "Set1")[i])
}
```

Group 2 Wright Maps.

```{r Wright_g2}

for (i in 1:length(scale_names_group2)){
  tmp_item_symbols <- matrix(rep(49:54, 
                               times = nrow(unimirt::ThurstonianThresh(
                                 grmit_g2_out2[[i]]$mirt.out))),
                              byrow = TRUE, 
                                ncol = (ncol(unimirt::ThurstonianThresh(
                               grmit_g2_out2[[i]]$mirt.out)))-1)
  tmp_item_colours <- matrix(rep(brewer.pal(6, "Dark2"), 
                               times = nrow(unimirt::ThurstonianThresh(
                                 grmit_g2_out2[[i]]$mirt.out))),
                             byrow = TRUE, 
                             ncol = (ncol(unimirt::ThurstonianThresh(
                              grmit_g2_out2[[i]]$mirt.out)))-1)
  tmp_thresh <- unimirt::ThurstonianThresh(grmit_g2_out2[[i]]$mirt.out)
  WrightMap::wrightMap(thetas = grmit_g2_out2[[i]]$personscores,
                       thresholds = tmp_thresh[,-1],
                       main.title = paste("Wright Map with Thurstonian Thresholds for ", scale_names_group2[i], sep = ""),
                       label.items = tmp_thresh[,1],
                       show.thr.lab = FALSE,
                       thr.sym.pch = tmp_item_symbols,
                       thr.sym.cex = 1.5,
                       thr.sym.col.fg = tmp_item_colours)
                       #dim.color = RColorBrewer::brewer.pal(8, "Set1")[i])
}
```

Now we drop Attain_7.

```{r Wright_g2b}

grmit_g2_out2_dropA7 <- MASDERtools::grmit(dat = group2, 
                                           scale.names = scale_names_group2[2],
                                           drop.items = list(7))


for (i in 1){
  tmp_item_symbols <- matrix(rep(49:54, 
                               times = nrow(unimirt::ThurstonianThresh(
                                 grmit_g2_out2_dropA7[[i]]$mirt.out))),
                              byrow = TRUE, 
                                ncol = (ncol(unimirt::ThurstonianThresh(
                               grmit_g2_out2_dropA7[[i]]$mirt.out)))-1)
  tmp_item_colours <- matrix(rep(brewer.pal(6, "Dark2"), 
                               times = nrow(unimirt::ThurstonianThresh(
                                 grmit_g2_out2_dropA7[[i]]$mirt.out))),
                             byrow = TRUE, 
                             ncol = (ncol(unimirt::ThurstonianThresh(
                              grmit_g2_out2_dropA7[[i]]$mirt.out)))-1)
  tmp_thresh <- unimirt::ThurstonianThresh(grmit_g2_out2_dropA7[[i]]$mirt.out)
  WrightMap::wrightMap(thetas = grmit_g2_out2_dropA7[[i]]$personscores,
                       thresholds = tmp_thresh[,-1],
                       main.title = paste("Wright Map with Thurstonian Thresholds for ", scale_names_group2[2], sep = ""),
                       label.items = tmp_thresh[,1],
                       show.thr.lab = FALSE,
                       thr.sym.pch = tmp_item_symbols,
                       thr.sym.cex = 1.5,
                       thr.sym.col.fg = tmp_item_colours)
                       #dim.color = RColorBrewer::brewer.pal(8, "Set1")[i])
}
```

Now we print tables of the Thurstonian Thresholds for the full IRT (without dropping any items).

```{r thurstone_tables}
thursty_g1 <- NULL
for (i in 1:length(scale_names_group1)){
  thursty_g1 <- rbind(thursty_g1, unimirt::ThurstonianThresh(grmit_g1_out2[[i]]$mirt.out))
}

thursty_g2 <- NULL
for (i in 1:length(scale_names_group2)){
  thursty_g2 <- rbind(thursty_g2, unimirt::ThurstonianThresh(grmit_g2_out2[[i]]$mirt.out))
}

print(thursty_g1)
print(thursty_g2)

write.csv(thursty_g1, file = "out/thursty-g1.csv")
write.csv(thursty_g2, file = "out/thursty-g2.csv")
```

Now we print the coefficients.

```{r coef_tables}
coefs_g1 <- NULL
for (i in 1:length(scale_names_group1)){
  tmp <- matrix(unlist(coef(grmit_g1_out2[[i]]$mirt.out))[1:(length(unlist(coef(grmit_g1_out2[[i]]$mirt.out)))-2)],ncol=7, byrow=TRUE)
  rownames(tmp) <- names(coef(grmit_g1_out2[[i]]$mirt.out))[-length(names(coef(grmit_g1_out2[[i]]$mirt.out)))]
  coefs_g1 <- rbind(coefs_g1, tmp)
}
coefs_g2 <- NULL
for (i in 1:length(scale_names_group1)){
  tmp <- matrix(unlist(coef(grmit_g2_out2[[i]]$mirt.out))[1:(length(unlist(coef(grmit_g2_out2[[i]]$mirt.out)))-2)],ncol=7, byrow=TRUE)
  rownames(tmp) <- names(coef(grmit_g2_out2[[i]]$mirt.out))[-length(names(coef(grmit_g2_out2[[i]]$mirt.out)))]
  coefs_g2 <- rbind(coefs_g2, tmp)
}
colnames(coefs_g1) <- colnames(coefs_g2) <- colnames(coef(grmit_g2_out2[[i]]$mirt.out)[[1]])
print(coefs_g1)
print(coefs_g2)
write.csv(coefs_g1, file = "out/grm-coefs-g1.csv")
write.csv(coefs_g2, file = "out/grm-coefs-g2.csv")
```